% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\hyphenation{pdfTeX Mathematica}

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Alexander H. Foss\\
 \line(1,0){470}\\
% [12pt] % the \\[12pt] adds a blank line after name
}
 
% blank "address" on left
\address{ 
}
\address{
    \hfill alexanderhfoss@gmail.com
}
 

\begin{resume} 
 
\section{Education} 
 {\bf University at Buffalo \hfill Aug 2012 -- May 2017 (anticipated)}\\
 Ph.D Candidate, Biostatistics \\
 GPA 3.9/4.0\\
 {\bf University of the South \hfill Aug 2010 -- May 2012}\\
 Post-baccalaureate student\\
 GPA 4.0/4.0\\
 {\bf University of California, Berkeley \hfill Aug 2009 -- Mar 2010}\\
 Ph.D Candidate, Psychology\\
 GPA 4.0/4.0\\
 Area of Focus: Cognition, Brain, and Behavior\\
 {\bf Indiana University, Bloomington    \hfill Aug 2003 -- Aug 2007}\\
 Bachelor of Science in Music and an Outside Field\\
 Graduated with High Distinction, GPA 3.9/4.0\\
 Major: Piano Performance\\ 
 Outside Field: Psychology, with Departmental Honors


\section{GRE Scores}
 {\bf General GRE scores}: 790 Quantitative, 730 Verbal, 5.5 Analytical Writing\\
 {\bf Psychology Subject GRE score}: 830


\section{Experience}

 {\bf University at Buffalo, Dept of Biostatistics}, Buffalo, NY\\
 {\it Research Assistant} \hfill {\bf June 2013 -- Present} \\
 Principal Investigator: Dr. Marianthi Markatou 
 \begin{itemize} \itemsep -2pt
  \item Implemented Monte Carlo simulation studies in R investigating the impact of measurement error on clustering methods with mixed categorical and continuous data
  \item Worked with collaborators at University at Buffalo and IBM Watson Labs
  \item Conducted a literature review on clustering methodologies focusing on mixed data types and measurement error
 \end{itemize}

 {\bf University at Buffalo, Dept of Biostatistics}, Buffalo, NY\\
 {\it Teaching Assistant} \hfill {\bf Fall 2012, Spring 2013}
 \begin{itemize} \itemsep -2pt
  \item Teaching assistant for STA527, Introduction to Medical Statistics, a graduate level introductory statistics course; and STA302, Introduction to Statistical Inference, an undergraduate level mathematical statistics course
  \item Led weekly recitation sections, held weekly office hours, graded homework, assisted in grading exams
  \item Received excellent student evaluations: 94\% agreement with the statement ``Presents material well,'' 80\% respondents categorizing overall teaching effectiveness as ``One of the best'' or ``Above Average'', and comments such as ``One of the best TAs I have had so far.'' (Spring 2013 evaluations)
 \end{itemize}
 
 {\bf University at Buffalo, Dept of Biostatistics}, Buffalo, NY\\
 {\bf Population Health Observatory}\\
 {\it Research Assistant} \hfill {\bf Summers 2010, 2011, 2012} \\
 Principal Investigator: Dr. Randolph Carter
 \begin{itemize} \itemsep -2pt
  \item Implemented a Monte Carlo simulation in R evaluating published 
        methods of calculating the lifetime risk at birth of Krabbe disease
        (paper accepted)
  \item Conducted a literature review for a paper describing a novel method 
        of calculating mortality rates of Krabbe disease and related diseases 
  \item Assisted in the writing of grant proposals to the NIDDK and HRSA,
        as well as an ARRA grant proposal.
 \end{itemize}

 {\bf New York University, Dept of Applied Psychology}, New York, NY\\
 Principal Investigator: Dr. Arnold Grossman\\
 {\it Data Analyst (part-time)} \hfill {\bf Mar 2011 -- June 2012}
 \begin{itemize} \itemsep -2pt
  \item Analyzed associations between domestic abuse, neglect and
        other variables in elderly LGBT adults, as well as associations
        between homelessness and traumatic life events in LGBT youth
  \item Co-author on a paper investigating the relationship between
        pubertal timing and sexual identity development (accepted)
 \end{itemize}

 {\bf University of California, Dept of Psychology}, Berkeley, CA\\
 {\bf Affective Cognitive Neuroscience Lab}\\
 Principal Investigator: Dr. Sonia Bishop\\
 {\it Graduate Student Researcher} \hfill {\bf Aug 2009 -- Apr 2010}
 \begin{itemize} \itemsep -2pt
  \item Assisted in the design and analysis of a functional MRI study 
        investigating neural processing of ambiguous and pure emotions 
  \item Assisted in the writing of an NIMH BRAINS research grant concerning
        anxiety reduction biofeedback training using real-time fMRI
 \end{itemize}

 {\bf Children's Hospital of Philadelphia}, Philadelphia, PA\\
 {\bf Developmental Neuroimaging Lab}\\
 Principal Investigator: Dr. Robert Schultz\\
 {\it Research Assistant (full time)} \hfill {\bf Oct 2007 -- Jun 2009}
 \begin{itemize} \itemsep -2pt
  \item Designed a study investigating the interaction of executive 
        functioning and neural adaptation in ventral visual areas
  \item Analyzed functional MRI and eye-tracking data using 
        BrainVoyager QX and MatLab; wrote C subroutines called from 
        within MatLab functions (MEX files)
 \end{itemize}

 {\bf Yale University School of Medicine}, New Haven, CT\\
 {\bf Developmental Neuroimaging Lab}\\
 Principal Investigator: Dr. Robert Schultz\\
 {\it Research Assistant (full time)} \hfill {\bf Jul 2007 -- Oct 2007}
 \begin{itemize} \itemsep -2pt
  \item Assisted in the design and implementation of fMRI studies of
        visual perception and social cognition
  \item Administered neuropsychological test to patients with autism spectrum
        disorders
 \end{itemize}

 {\bf Indiana University, Dept of Psychological \& Brain Sciences}, Bloomington, IN\\
 {\bf Cognition \& Action Neuroimaging Lab}\\
 Principal Investigator: Dr. Karin James\\
 {\it Undergraduate Research Assistant} \hfill {\bf Sep 2005 -- Aug 2007}
 \begin{itemize} \itemsep -2pt
  \item Designed, analyzed, and published results of an fMRI experiment 
        investigating the neural correlates of auditory perception of tone 
        combinations; analysis conducted using BrainVoyager QX
 \end{itemize}
 

\begin{tabbing}
\section{Publications}
 {\bf Foss} \= {\bf AH}, Duffner PK, \& Carter RL (2013). Lifetime Risk Estimators in Epidemiolo-- \\
 \> gical Studies of Krabbe Disease: Review and Monte Carlo Comparison. \\
 \> {\it Rare Diseases} 1(2), e25212. \\

 {\bf Foss} {\bf AH}, Altschuler EL, \& James KH (2007). 
 Neural correlates of pythagorean\\ 
 \> ratio rules. {\it Neuroreport} 18, 1521-1525.\\

 Barczykowski AL, {\bf Foss AH}, Duffner PK, Yan L, \& Carter 
 RL (2012). Death rates \\
 \> in the U.S. due to Krabbe disease and related leukodystrophy and 
 lysosomal \\
 \> storage diseases. {\it American Journal of Medical Genetics Part A} 158A, 2835-2842.\\

  Grossman AH, {\bf Foss} {\bf AH}, D'Augelli AR. 
  Puberty: Maturation, Timing and Adjustment, \\
  \> and Sexual Identity Developmental Milestones among Lesbian, Gay, and Bisexual  \\
  \> Youth. (accepted, {\it Journal of LGBT Youth}) \\

% Barczykowski AL, Jalal K, Duffner PK, {\bf Foss AH}, \& Carter
% RL. Age specific\\
% \> incidence of Krabbe disease from 0-5 years of
% age. (In preparation)\\
%
 Tan W, Jalal K, {\bf Foss AH}, Duffner PK, \& Carter RL. Race
 effects on age specific\\
 \> metachromatic leukodystrophy incidence
 among 0-5 year olds. (In preparation)
\end{tabbing}


\begin{tabbing}
\section{Posters}

 {\bf Foss} \= {\bf AH}, Duffner PK, \& Carter RL (2013). Lifetime Risk Estimators in Epidemi-- \\
 \> ological Studies of Krabbe Disease: Review and Monte Carlo Comparison. \\
 \> {\it Joint Statistical Meetings}, Montreal, Canada. \\

 Nu\~{n}ez-Elizalde A, {\bf Foss AH}, Aguirre G, \& Bishop SJ 
 (2010). Does he look scared \\
 \> to you? Effects of trait anxiety upon neural dissimilarity 
 measures for ambi-\\
 \> guous and pure emotional expressions. {\it Vision Sciences 
 Society}, Naples, FL,\\
 \> USA.\\

 Herrington JK, Grupe DW, Hunyadi ET, Shin CS, {\bf Foss AH}, 
 Taylor JM, \& Schultz\\
 \> RT (2010). Fusiform gyrus and face processing: Intrasubject 
 stability, hemi-\\
 \> spheric asymmetry, and effective connectivity. {\it 
 International Meeting for}\\
 \> {\it Autism Research}, Philadelphia, PA, USA.\\

{\bf Foss}  {\bf AH} \& James KH (2006). Music and language 
 processing: Investigating the\\
 \> neural correlates of expertise. {\it Human Brain Mapping 
 Conference}, Chicago, IL,\\
 \> USA.

\end{tabbing}


\section{Academic \\ Honors} 
\begin{itemize} \itemsep -2pt
 \item Perry Poster Award, University at Buffalo (\$100) \hfill April 19, 2013
 \item Honorable Mention, NSF GRF Program \hfill Spring 2013
 \item Presidential Fellowship, University at Buffalo (\$23,000) \hfill Fall 2012
 \item Diebold Fellowship, UC Berkeley Psychology Dept (\$14,600) \hfill Fall 2009
 \item Excellence in Research Award, IU Psychology Dept \hfill April 19, 2007
 \item Honors Thesis Award, IU Honors College \hfill Spring 2007
 \item Capstone Grant, Howard Hughes Medical Institute (\$4,250) \hfill Spring 2006
 \item Membership, {\it Psi Chi}, IU chapter \hfill Spring 2006
 \item Metz Scholarship, IU Honors College (\$56,000) \hfill Fall 2003
 \item Merit scholarship, IU School of Music (\$40,000) \hfill Fall 2003
\end{itemize}
 

% Tabulate computer skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
   \rule{0cm}{.5cm}
    \underline{Languages:} & R, Bash, C, Java, Mathematica, MATLAB, 
                             Processing, Python, Visual Basic, HTML/XHTML,
                             CSS\\
   \rule{0cm}{.5cm}
    \underline{Software:} & SPSS/PASW, SAS, BrainVoyager QX 1.10, pdf\TeX{}, 
                            Sweave, Adobe Photoshop 7.0, VIM, 
                            OpenOffice/LibreOffice, MS Office Suite\\
   \rule{0cm}{.5cm}
    \underline{Operating Systems:} & Windows (98/XP/Vista/7),
                                     Macintosh (OS9, OSX),
                                     Linux (Red Hat, Ubuntu, CentOS)
   \end{tabular}


%\section{Relevant Coursework}
% {\bf University at Buffalo:} Regression Analysis (STA503),
%  Math Analysis for Biostatisticians (STA511), Introduction to Theoretical
%  Statistics I (STA521) \\
% {\bf University of the South:} Probability and Statistics I (MATH 321),
%  Multidimensional Calculus (MATH 207), Linear Algebra (MATH 210), 
%  Discrete Mathematical Structures (MATH 215), Genomics (BIOL 381),
%  Probability and Statistics II (MATH 322),
%  Numerical Analysis (MATH 301) \\
% {\bf UC Berkeley:} Methods in Biological Psychology (PSYCH 210A),
%  Functional MRI Methods (PSYCH 214), Neuroimaging Seminar Series
%  (PSYCH 290B)\\


\section{Other Proficiencies}
\begin{itemize} \itemsep -2pt
 \item Fluent in Spanish
 \item Classically-trained pianist, freelance organist
\end{itemize}


\section{Community Service}
{\bf New York State Center of Excellence in Bioinformatics and Life Sciences} \\
 {\it Volunteer Speaker} \hfill {\bf July 24, 2012}
 \begin{itemize} \itemsep -2pt
  \item Gave a presentation on face recognition, brain imaging, and autism to a group of exchange students
 \end{itemize}

{\bf The Franklin Institute Museum of Science}, Philadelphia, PA\\
{\it Volunteer} \hfill {\bf Nov 2007 -- Oct 2008}
 \begin{itemize} \itemsep -2pt
  \item Conducted science demonstrations including paper-making, the ``brain bar'' neuroscience exhibit, and the Baldwin 60,000 steam engine simulation
  \item Interacted individually with children ages 4--16 and their parents
 \end{itemize}

{\bf Wonderlab Museum of Science}, Bloomington, IN\\
{\it Volunteer} \hfill {\bf May 2006 -- Jul 2007}
 \begin{itemize} \itemsep -2pt
  \item Conducted ``science-on-the-spot'' demonstrations
  \item Interacted individually with children ages 4--12 and their parents
 \end{itemize}

{\bf International Service Learning}, Kansas City, MO/San Jose, Costa Rica\\
{\it Volunteer} \hfill {\bf Mar 10 -- 18, 2007}
 \begin{itemize} \itemsep -2pt
  \item Helped set up clinics in Costa Rica in the towns of Tib\'{a}s and Puntarenas
  \item Conducted community triage, took patient histories, gave eye examinations, and prescribed reading glasses
 \end{itemize}


\end{resume} 
\end{document} 


